An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-07-15 neurips-19/poly-embed.tex
arXiv edits updating top k section from Jessie

\subsection{Inconsistency of top-$k$ losses}

\btw{The story we discussed: YK show $L'$ is inconsistent.  Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?  (It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}

In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
\begin{align}\label{eq:top-k}
  \elltopk(r,y) = \Ind{y \not \in r}~,
\end{align}
which simply gives a penalty if the label was not in the reported set.

Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
\begin{align}\label{eq:L-2-surrogate}
  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
\end{align}
where $e_y$ is $1$ in component $y$ and 0 elsewhere.

With our framework, we can say more.
Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
We therefore turn to deriving this discrete loss $\ell'$.

In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix... remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
From Lemma~\ref{lem:loss-restrict}\raft{was lem:top-k-surrogate-embeds}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
\begin{align}\label{eq:ell-2}
\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
\end{align}
We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.

Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
Writing the expected loss, we have
%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
So let us ask when it is better to drop an element $i$ from $r$:
% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.

% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.

% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.

%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.

@@

\begin{lemma} \label{lemma:exposed-shortest}
  Let $U$ be a convex, closed set and $u \not\in U$.
  Then $\inf_{u^* \in U} \|u-u^*\|$ is achieved by some unique $u^* \in U$.
  Furthermore, $u^*$ is the unique member of $U$ such that $u = u^* + \alpha v$ for some $\alpha > 0$ and unit vector $v$ that exposes $u^*$.
\end{lemma}
\begin{proof}
  Unique achievement of the infimum is well-known.
  (Achievement follows e.g. because the set $U \cap \{u' : \|u - u'\| \leq d(U,u) + 1\}$ is closed and compact, so the continuous function $u' \mapsto \|u-u'\|$ achieves its infimum.
  Uniqueness follows because for two different points $u',u''$ at the same distance from $u$, the point $0.5u' + 0.5u''$ is strictly closer and also lies in the convex set $U$.)
  Now suppose $u = u' + \alpha' v'$ where $v'$ is a unit vector exposing $u'$.
  Then $U$ is contained in the halfspace $\{u'': \langle u'', v'' \rangle \leq \langle u',v' \rangle \}$.
  But every point in this halfspace is distance at least $\alpha'$ from $u$, as $\|u-u''\| \geq \langle v, u - u'' \rangle \geq \langle v, u-u'\rangle = \alpha'$.
  So $u'$ uniquely achieves this minimum distance.
\end{proof}

\begin{lemma} \label{lemma:distance-loss}
  \raft{What I changed: linear ftn $\to$ affine; name the cell $U_f$ for $f$; also name set of functions $\F$, normals $V_f$, etc}
  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq c \cdot d(\Gamma(p),u) . \]
\end{lemma}
\begin{proof}
  Fix $p$ and let $U = \Gamma(p)$.
  If $u \in U$, then both sides are zero.
  So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.

  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many affine functions.
  Recall that $\risk{L}(p) = \min_{u} L(u;p)$, the Bayes risk.
  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the maximum those affine functions that are never equal to $L$ for any $u^* \in U$.
  We have $\hat{L}(u^*;p) = \risk{L}(p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
  Now $\hat{L}$ is also a maximum over finitely many affine functions $\F$.
  Each such function $f\in\F$ is equal to $\hat{L}$ above a closed, convex cell $U_f\subseteq\reals^d$ in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
  If $f$ has nonzero gradient, then $U_f \cap U$ is a face of $U$.
  We will prove that there exists $c_f > 0$ such that, for all $u\in U_f$,
    \[ \hat{L}(u;p) \geq \risk{L}(p) + c_f \cdot d(U,u) . \]
  Taking $c$ to be the minimum of $c_f$ over the finitely many $f\in\F$ with nonzero gradient (which covers all points $u \not\in U$) will complete the proof.

  Consider the set of unit vectors $V = \{v \in \reals^d : \|v\|=1\}$ and the boundary of $U$, denoted $\partial U$.
  For any $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, let\raft{I'm not actually sure what definition of ``exposes'' we are using here; I think we just mean that $v$ is normal to $U$ at $u^*$, right?}
    \[ G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\} . \]
  %Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
  We will prove the following steps:
  \begin{enumerate}
    \item For all $u^*\in\partial U$, $v\in V$ such that $v$ exposes $u^*$, there is some $f\in\F$ such that $G_{u^*,v}\subseteq U_f$.
    \item For all $v\in V$, there exists a constant $c_{v} > 0$ such that $L(u) = \risk{L}(p) + c_{v} \cdot d(U,u)$ for all $u \in G_{u^*,v}$ and all $u^*$ exposed by $v$.
    \item For all $f\in \F$, the set $V_f = \{v\in V : \exists u^*\in\partial U\: G_{u^*,v} \subseteq U_f\}$ is compact (closed and bounded), and the map $v \mapsto c_{v}$ is continuous on $V_f$.
    \item Hence, there is an infimum $c_f > 0$ such that $f(u) \geq \risk{L}(p) + c_f \cdot d(U,u)$ for all $u\in U_f$.
    \item Taking $c = \min \{c_f : f\in\F, \nabla f \neq 0\}$, we obtain $L(u;p) \geq \hat{L}(u;p) \geq \risk{L}(p) + c \cdot d(U,u)$ for all $u \not\in U$.
  \end{enumerate}

  (1) Follows because $G_{u^*,v}$ is contained in a cell of the power diagram, which is a set of points where $\hat{L}(\cdot;p) = f(\cdot)$. \bo{Should have more justification.}

  (2) Let $\nabla f$ denote the gradient of the affine function $f$.
  Note that because $u^*$ is on the boundary of $U$, we have $f(u^*) = \hat{L}(u^*;p) = \risk{L}(p)$.
  So we can write, using Lemma \ref{lemma:exposed-shortest},
  \begin{align*}
    f(u) &= f(u^*) + (\nabla f)\cdot (u - u^*)  \\
    f(u) &= f(u^*) + (\nabla f)\cdot (d(u^*,u) v)  \\
         &= \risk{L}(p) + c_{v} \cdot d(U,u)  \\
  \end{align*}
  where $c_{v} = (\nabla f)\cdot v$.
  We must have $c_{v} > 0$ because the set $U$ minimizes $L(\cdot;p)$, so $f(u) > f(u^*) = \risk{L}(p)$.

  (3) The intersection $U_f \cap U$ is a face of $U$.
  $V_f$ is simply the union of normal cones $N_U(u^*)$ intersected with $V$ for all $u^* \in U_f \cap U$; as normal cones are identical in the relative interiors of faces, and $U_f\cap U$ is the union of finitely many such relative interiors of faces, $V_f$ is union of finitely many closed convex sets, and thus closed.
  \raft{This could stand a more formal treatment}
  Boundedness follows as $V$ is bounded.

  Finally, steps (4) and (5) are immediate.
\end{proof}

>>>>

\subsection{Inconsistency of top-$k$ losses}
% 7.14.19- proposed version for arXiv
\btw{The story we discussed: YK show $L'$ is inconsistent.  Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?  (It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}

In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.

Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $u_{[i]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
\begin{align}\label{eq:L-2-surrogate}
L_k(u)_y := \left( 1-u_y + \tfrac{1}{k} \textstyle\sum_{i=1}^k (u - e_y)_{[i]} \right)_+~,
\end{align}
where $e_y$ is $1$ in component $y$ and 0 elsewhere.

For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
%Without loss of generality, suppose $u$ is sorted in decreasing order, i.e. $u_1 \geq u_2 \geq u_3 = 0$ by invariance in the $\ones$ direction, shown in the Appendix.
We can re-write $L_2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
One can verify that for every distribution $p \in \Delta_3$, $\inprod{p}{L}$ has a minimizer in the set $\R'$ composed of the tuples $i$ given by $\Gamma_i$ in Figure~\ref{fig:convex-surrogate-top-k}.

%transition here
\begin{figure}
\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/original-top-k}
	\caption{The minimizers of the $top-2$ loss $\ell_{top-2}$ as a function of $p$.}
	\label{fig:original-top-k}
\end{minipage}
\hfill
\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/convex-surrogate-top-k}
	\caption{Level sets for the minimizers of $\inprod{p}{L(\cdot)}$.}
	\label{fig:convex-surrogate-top-k}
\end{minipage}
\hfill
\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
	\caption{The finite property $\prop{L|_\R}$}
	\label{fig:finite-surrogate-top-k}
\end{minipage}
\end{figure}

Figure~\ref{fig:original-top-k} gives a map of the property values of $\gamma_{top-2} := \prop{\ell_{top-2}}$ over the domain, $\Delta_3$, where $\ell_{top-2}(r)_y = \Ind{y \not\in r}$.
(Each cell in this simplex is a level set $\gamma_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\ell_{top-2}}$.)
Moreover, Figure~\ref{fig:convex-surrogate-top-k} maps the property $\Gamma := \prop{L_2}$ over $\Delta_3$.
By visual inspection, we can observe there is no ``refining'' mapping from $\gamma_{top-2}$ to $\Gamma$.
By refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\Gamma_i = \gamma_{top-2,j}$.
If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L_2$ embeds $\ell_{top-2}$.

However, by Theorem~\ref{thm:poly-embeds-discrete}, we do know that $L_2$ embeds some discrete loss $\ell_2 := L_2|_\R$ since it is polyhedral; the level sets of $\prop{\ell_2} $ are shown in Figure~\ref{fig:finite-surrogate-top-k}.
\jessie{I can't find a nice reduction of this loss for reports with a $2$ in the vector.}
At first glance, these properties seem indentical, but $\prop{L_2}$ has an infinite number of level sets at each distribution, not shown in Figure~\ref{fig:convex-surrogate-top-k} for simplicity.
We can ``refine'' $\prop{L_2}$ down to $\prop{\ell_2}$ by the axiom of choice.

\jessie{Not sure if this is too much detail...}
For intuition, since $\prop{\ell}$ does not refine $\prop{L}$, then $L$ does not embed $\ell$.
For example, we can take two distributions $p_1 \in \gamma_{top-2, \{1,1,0\}}$ and $p_2 \in \gamma_{top-2, \{1,0,1\}}$ such that $p_1, p2 \in \Gamma_{(1,0,0)}$.
Regardless of the choice of $\psi((1,0,0))$, for either $p_1$ or $p_2$, $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\ell_{top-2}(u)}$.
Thus, we see that $L_2$ is not a consistent surrogate for $\ell_{top-2}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% old version submitted to NuerIPS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\btw{The story we discussed: YK show $L'$ is inconsistent.  Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?  (It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
%
%In certain classification problems, for example in information retrieval, it is common to predict a set of possible labels.
%As one instance, for $k<n$ the top-$k$ classification problem has reports $\R := \{r \subseteq [n] : |r| = k\}$, with label $y \in [n]$.
%The natural discrete loss $\elltopk:\R \to \reals^\Y_+$ is given by
%\begin{align}\label{eq:top-k}
%  \elltopk(r,y) = \Ind{y \not \in r}~,
%\end{align}
%which simply gives a penalty if the label was not in the reported set.
%
%Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
%\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
%\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
%\begin{align}\label{eq:L-2-surrogate}
%  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
%\end{align}
%where $e_y$ is $1$ in component $y$ and 0 elsewhere.
%
%With our framework, we can say more.
%Specifically, while $(L',\psi)$ is not consistent for $\elltopk$, since $L'$ is polyhedral (Lemma~\ref{lem:top-k-polyhedral}), we know from Theorem~\ref{thm:poly-embeds-discrete} that it embeds \emph{some} discrete loss $\ell'$, and from Theorem~\ref{thm:eps-thick-calibrated} there is a link $\psi'$ such that $(L',\psi')$ is calibrated (and consistent) for $\ell'$.
%We therefore turn to deriving this discrete loss $\ell'$.
%
%In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix... remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
%From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors:
%\begin{align}\label{eq:ell-2}
%\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}| = (1+\tfrac 1 k)\Ind{y \not\in r} + \tfrac 1 k (|r|-1)~.
%\end{align}
%We now see that $\ell'$ is essentially $\elltopk$ (extended to sets smaller than $k$) plus an additional cardinality term which rewards smaller sets.
%
%Knowledge of what loss $L'$ actually embeds greatly simplifies the task of proving inconsistency with $\elltopk$.
%Specifically, we see that $\ell'$ allows sets of cardinality strictly less than $k$, so we can look for a distribution making one of these smaller sets optimal.
%Writing the expected loss, we have
%%$\inprod{p}{\ell'(r)} = 1 - p(r) + \tfrac 1 k (|r|-p(r)) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$,\\
%$\inprod{p}{\ell'(r)} = (1+\tfrac 1 k)(1 - p(r)) + \tfrac 1 k (|r|-1) = 1 + \tfrac 1 k |r| - (1 + \tfrac 1 k) p(r)$, where $p(r) = \sum_{i\in r} p_i$.
%% It is now easy to see that the optimal $r$ for any fixed cardinality $|r|=c$ is the $c$ most likely labels.
%So let us ask when it is better to drop an element $i$ from $r$:
%% If $i$ is the index of the $c$th most likely label (so $p_i = p_{[c]}$)
%we have $\inprod{p}{\ell'(r)-\ell'(r\setminus\{i\})} = \tfrac 1 k - (1+\tfrac 1 k)p_i$, meaning we will drop elements from $r$ until they all have weight at least $\tfrac 1 {k+1}$.
%In particular, for distributions close to uniform, $r=\emptyset$ is optimal, already giving us inconsistency\raft{If space (nope) we should spell this out like Jessie did: however ties are broken at $u=0$, pick a distribution with bumps going against the ties, and $u=0$ is still optimal.}.
%More generally, as $k < n$, the set $P = \{p\in\simplex : \max_{r\in\R'} p(r) < k/(k+1)\}$ is full-dimensional and guarantees that at least one of the top $k$ labels has probability strictly less than $\tfrac 1 {k+1}$.
%
%% We now focus on the case where $k=1$; the top-$k$ loss reduces to 0-1 loss in this case.
%% To show a set of distributions where $\prop{\ell'}(p) \neq \prop{\elltopk}(p)$, we claim that $\vec{0}~\in~\prop{\ell'} \implies \risk{\ell'}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
%% Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1 \implies \vec{0} \not\in \prop{\elltopk}(p)$.
%
%% First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
%% Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell'(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$.
%% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
%% Therefore, we have that $\vec{0} \in \prop{\ell'}(p)$ but $\vec{0} \not\in \prop{\elltopk}(p)$ for any $p$ such that $\max_y p_y \leq 1/2$.
%
%
%
%%Since we can see that $\ell' \neq \elltopk$, we can then see that $L'$ is not consistent with respect to $\elltopk$.
%%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell'$.
%%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.

@@

%Bo new
\begin{lemma} \label{lemma:exposed-shortest}
  Let $U$ be a convex, closed set and $u \not\in U$.
  Then $\inf_{u^* \in U} \|u-u^*\|$ is achieved by some unique $u^* \in U$.
  Furthermore, $u^*$ is the unique member of $U$ such that $u = u^* + \alpha v$ for some $\alpha > 0$ and unit vector $v$ that exposes $u^*$.
\end{lemma}
\begin{proof}
  Unique achievement of the infimum is well-known.
  (Achievement follows e.g. because the set $U \cap \{u' : \|u - u'\| \leq d(U,u) + 1\}$ is closed and compact, so the continuous function $u' \mapsto \|u-u'\|$ achieves its infimum.
  Uniqueness follows because for two different points $u',u''$ at the same distance from $u$, the point $0.5u' + 0.5u''$ is strictly closer and also lies in the convex set $U$.)
  Now suppose $u = u' + \alpha' v'$ where $v'$ exposes $u'$.
  Then $U$ is contained in the halfspace $\{u'': \langle u'', v'' \rangle \leq \langle u',v' \rangle \}$.
  We claim $u'$ is the closest point in this halfspace to $u$,\bo{seems obvious, should be proven} so the distance of $u$ to this halfspace equals its distance to $u'$ which equals its distance to $U$.
  We have already seen that this distance is uniquely achieved by $u' = u^*$.
\end{proof}
%end Bo new

\begin{lemma} \label{lemma:distance-loss}
  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq c \cdot d(\Gamma(p),u) . \]
\end{lemma}
\begin{proof}
  Fix $p$ and let $U = \Gamma(p)$.
  If $u \in U$, then both sides are zero.
  So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.

  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many linear functions.
  Construct the convex polyhedral function $\hat{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
  We have $\hat{L}(u^*;p) = L(u^*;p)$ for all $u^* \in U$ and $\hat{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
  Now $\hat{L}$ is the max over a finite number of linear functions.
  Each such function $f$ with gradient $\nabla f$ is equal to $\hat{L}$ above a closed, convex cell in the power diagram formed by projecting $\hat{L}(\cdot;p)$.
  If $f$ has nonzero gradient, its cell overlaps with $U$ exactly at some face of $U$.
  We will prove that there exists $c_f > 0$ such that, for all $u$ in the corresponding cell of the power diagram,
    \[ \hat{L}(u;p) \geq L(u^*;p) + c_f \cdot d(U,u) . \]
  We will then repeat this for the finitely many $f$ with nonzero gradient (which covers all points $u \not\in U$) and take the minimum to obtain the desired $c > 0$.

  Consider the set of unit vectors $\{v \in \reals^d : \|v\|=1\}$ and the set of $u^*$ on the boundary of $U$.
  For all pairs $u^*,v$ such that $v$ exposes $u^*$, let
    \[ G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\} . \]
  Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
  We claim each $G_{u^*,v}$ can be associated with at least one linear $f$ such that $f(u) = \hat{L}(u;p)$ for all $u \in G_{u^*,v}$.
  \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\hat{L}$.}
  Hence for all $u$ in $G_{u^*,v}$, we have
  \begin{align*}
    \hat{L}(u;p) &= \hat{L}(u^*;p) + (\nabla f) \cdot (d(u^*,u) v)  \\
                      &= L(u^*;p) + c_{u^*,v} \cdot d(U,u)
  \end{align*}
  where $c_{u^*,v} := (\nabla f) \cdot v$, and we note $u^* = \min_{u' \in U} d(u',u)$. \bo{Should prove this; ought to follow because $v$ exposes $u^*$.}
  We must have $c_{u^*,v} > 0$, otherwise $G_{u^*,v} \subseteq U$ which is a contradiction.

  Now for each $f$, we claim the set $\{u^*, v : \text{$G_{u^*,v}$ is associated with $f$}\}$ is closed.
  This follows because the set of $u^*$ such that $f(u^*) = \hat{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
  The set is also bounded and the map $(u^*,v) \mapsto (\nabla f)\cdot v =: c_{u^*,v}$ is continuous, so the infimum over all positive $c_{u^*,v}$ is achieved by some positive member $c_f > 0$.
\end{proof}
